---
title: "Nico T"
---

```{r}
# Importing libraries and data set
library(tidyverse)
library(DataExplorer)
library(gtsummary)
demographics <- read.csv("../data/raw/data1/acs2017_county_data.csv")
```
# Looking at our variables
### First Observations
```{r}
head(demographics)
dim(demographics)
```

```{r}
demographics %>%
   mutate(across(where(is.character), as.factor)) %>% 
   summary()
```


> It looks like we have 3220 counties with 37 varibles. Two are characters, and the rest are doubles or integers respectively. The race variables seem to measure the percentage of a county is said race. Some of the variables are measured in percentages while others are measured in counts.

#### Looking at the counties with 100 percent white or hispanic populations

This seems odd because I would assume that very little communities in the united states would have homogeneous populations.

```{r}
demographics |> 
  filter(White == 100 | Hispanic == 100)
```

> These communties also report that the populations of the other groups are 0, so I am not concerned with these values.

### Missing Values
```{r}
plot_missing(demographics)
```

> It appears that we have 1 missing value in the child poverty variable

### Looking at the missing data

```{r}
demographics |> 
  filter(is.na(ChildPoverty))
```

> We might want to look further into how to solve for this missing value

```{r}
plot_histogram(demographics)
```

> Here we can see how some groups are minorites, but what is mre interesting is to see how they look different in communities with different levels of demographics in there population.

# Looking at relationships

```{r}
plot_correlation(demographics)
```

```{r}
plot_scatterplot(split_columns(demographics)$continuous, by = "White", sampled_rows = 1000L)
```


```{r}
plot_scatterplot(split_columns(demographics)$continuous, by = "Black", sampled_rows = 1000L)
```


> It looks like an interesting variable to explore is the employment status compared to different races. Also looking at thngs like how do people of different demographics get to work would also be an instesting thing to observe as well. Since the plots and correlation meter show that they are highly related. We can also find plenty of information to make a good data story with this information
